Literature Review - Informal

### 2019-11-28 Literature Review/Literature Review - Informal/sample.tex
Updated MPC research section

\textbf{Francesco: I've moved this to the top for your attention - it seems to be the most
interesting problem with the scope to improve the theoretical results as well as applications in
complex domains which are of significant interest these days.}

@@

@@

Since the review was written in 2016, there have been a number of approaches towards solving some of
these problems, most notably the intractability of the chance contraints. For instance, in 
\cite{Paulson2019}, Paulson and Mesbah propose the use of joint chance constraints in considering
time varying stochastic disturbances as well as model uncertainty. This is shown to be strongly
suited to non-linear systems, which itself is an open problem in the MPC sphere.

@@

>>>>

\textbf{Francesco: I've moved this to the top for your attention - it seems to be the most
interesting problem with the scope to improve the theoretical results as well as applications in
complex domains which are of significant interest these days. I will be adding in the
state-of-the-art review as we go along, but for now the general overview and research directions
are provided.}

@@

\subsection*{Model Predictive Control}

@@

Since the review \cite{Mesbah2016} was written in 2016, there have been a number of approaches towards solving
some of
these problems, most notably the intractability of the chance contraints. For instance, in 
\cite{Paulson2019}, Paulson and Mesbah propose the use of joint chance constraints in considering
time varying stochastic disturbances as well as model uncertainty. This is shown to be strongly
suited to non-linear systems, which itself is an open problem in the MPC sphere.

@@

the following presents a consideration of the applied end of MPC problems. I have tried to focus on
the domain independent suggestions, since the domain specific ones are virtually limitless.

\begin{itemize}
	\item Mean-field predictive control. Consider the case of a hybrid system, in which many components
	interact with each other. In addition, we may consider that there are multiple known disturbances
	acting on the system. This, at first seems like an impossible problem to solve due to the many
	interactions between all elements of the system. However, we can consider this as a game
	theoretic problem in which the components and the disturbances are players. The relatively new
	class of 'mean-field games' is a method which allows the many body problem to be approximated as
	a series of two-agent problems \cite{Yang2018}. Whilst the concerns in the 'Distributed
	predictive control' remain, this may prove to be a valuable area of applied research.
	\item Swarm control. Swarms often have simpler control rules implemented within each agent,
	which emerge into more complex results. It would be interesting to consider the application of
	robust and stochastic MPC with the aim of improving swarm results and satisfying constraints of
	the emergent phenomenon. This would be of particular interest in the case where the swarm has to
	track multiple objectives. A prediction of the swarm evolution may prove beneficial to ensure
	that all agents comply with the expected behaviour as the swarm switches tasks. Similarly, an
	adaptive stochastic model would be interesting to examine here to remain robust to agent
	failures in the group.
\end{itemize}
